---
title: "vignette - chunkfactory"
author: "irene cruz"
date: "`r format(Sys.time(), '%d-%m-%y')`"
output:
  html_document:
    df_print: paged
    highlight: tango
    code_folding: hide
    number_sections: true
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# Objectives
The package `chunkfactory`is meant to facilitate the production of documents for the exploration of bivariate descriptive statistics. 

It solves 2 questions: 
- repetitive code 
- presenting figures when repeating functions on a list

# Examples
```{r}
library(chunkfactory)
library(tidyverse)
```

```{r}
utils::data(package = "palmerpenguins", "penguins")
penguins$pes <- 1
```

## Bivariates by sex {.tabset}
```{r}
myres <- fabrica_chunks(
  vd = c("bill_length_mm", "bill_depth_mm", "flipper_length_mm"), 
  vi = c("sex"), 
  d = "penguins", 
  w = "pes")
```

`myres` generates a vector character containing the code that will be later evaluated with `knit_child` 

`r knitr::knit_child(text = unlist(myres))`


## Bivariates by island {.tabset}
```{r}
myres <- fabrica_chunks(
  vd = c("sex", "species"), 
  vi = c("island"), 
  d = "penguins", 
  w = "pes")
```

`r knitr::knit_child(text = unlist(myres))`

