---
title: "vignette - chunkfactory"
author: "irene cruz"
date: "`r format(Sys.time(), '%d-%m-%y')`"
output:
  html_document:
    df_print: paged
    code_folding: show
    highlight: tango
    number_sections: true
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE)
```

```{r}
library(chunkfactory)
library(tidyverse)
```

```{r}
utils::data(package = "palmerpenguins", "penguins")
penguins$pes <- 1
```


# Objectives
The package `chunkfactory`is meant to minimize the coding for markdown documents where a handful of functions need to be executed iteratively. This could facilitate, for instance, the production of documents for the exploration of bivariate descriptive statistics. 

It solves 2 problems: 

* repetitive code when performing the same operations on multiple combinations of variables
* presenting figures and tables in RMD when repeating functions on a list

The chunk factory can be applied to custom functions, or can be used with the built-in descriptive statistics functions for weighted data. Let's see the two cases. 

# Execute any function as a chunk factory {.tabset}

1. We can use the chunk factory on any custom function that generates the collection of results we need. The only restriction is that the `data` argument needs to be passed as a **text string**. Then the function needs to evaluate the text string. 

For example, we'll build a function that, for every pair of variables returns: 

* a linear regression model
* a formatted table of model results
* a tibble of model coefficients
* a predicted means plot

```{r}
myfunc <- function(data_name, v1, v2){
  data <- get(data_name)
  
  myformula <- as.formula(glue::glue("{v1} ~ {v2}"))
  res1 <- lm(myformula, data = data)
  res2 <- sjPlot::tab_model(res1, use.viewer = F)
  res3 <- broom::tidy(res1)
  res4 <- sjPlot::plot_model(res1, type = "eff", terms = v2)
  
  return(list(res1, res2, res3, res4))
}
```


If we were to simply execute `myfunc()`and get the list of results it produces as is, we'd find each element is preceded by the aesthetically unpleasant `[[x]]`, and table outputs are not printed following document guidelines (i.e. paged data frames): 

```{r}
myfunc("penguins", "flipper_length_mm", "species")

```

chunkfactory will help us reproduce results in an optimal way for a rmd document, while minimising the iteration of code. 

2. In order to create a chunk factory, first we'll need to define a list of parameters to iterate upon. Remember that the parameters need to be named exactly as the function arguments' names, and follow the same order: 

```{r}
myfunc_params <- list(
  data_name = "penguins", 
  v1        = c("flipper_length_mm", "bill_length_mm"),
  v2        = c("species", "island", "sex")
  )
```

Next we'll only need to execute our custom function with our list of parameters: 

```{r}
myres <- fabrica_chunks_myfunc(
  myfunc = myfunc, 
  param_list = myfunc_params, 
  title_level = 2)
```

This generates a character vector containing the markdown, chunks and code to be evaluated. See a sample:

```{r}
head(myres)
```

3. The list of results is then interpreted by `knit_child()`, like in the previous example:

`r knitr::knit_child(text = unlist(myres))`



# Examples with built-in functions

The package includes built-in functions in order to perform bivariate analyses with weighted data. 

If the dependent variable is numeric, results will show: 

* grouped descriptive statistics
* grouped boxplots

If the dependent variable is categorical, results will show:

* a cross-tab in tidy format, including adjusted-standardized residuals [citation]
* stacked bar chart

Results are organized into tabsets, like in the following example: 

## Bivariates by sex {.tabset}
```{r}
myres <- fabrica_chunks(
  vd = c("bill_length_mm", "bill_depth_mm", "flipper_length_mm"), 
  vi = c("sex"), 
  d = "penguins", 
  w = "pes")
```

`myres` generates a vector character containing the code that will be later evaluated with `knit_child` 

`r knitr::knit_child(text = unlist(myres))`


## Bivariates by island {.tabset}
```{r}
myres <- fabrica_chunks(
  vd = c("sex", "species"), 
  vi = c("island"), 
  d = "penguins", 
  w = "pes")
```

`r knitr::knit_child(text = unlist(myres))`
